---
title: "RMarkDocument"
author: "CDAC Noida"
date: "2024-01-02"
output: html_document
---

Plain text is added like this

to start the new paragraph just add two spaces at the end of the line  

*italics* CDAC *italics*

**bold** NOIDA **bold**

superscript^2^

~~strickthrough~~

[link](https://r4ds.had.co.nz/r-markdown.html#:~:text=R%20Markdown%20provides%20an%20unified,files%2C%20slideshows%2C%20and%20more.)

# Header 1

## Header 2

### Header 3

#### Header 4

##### Header 5

###### Header 6

endash: --

emdash: ---

ellipsis: ...

inline equation: $A = \pi*r^{2}$

horizontal rule (or slide break):

--------------------------------------------------------------------------------

> block quote

-   unorderedlist
-   item 1
    -   sub item 1
    -   sub item 2
-   item 2
    -   sub item 1
    -   sun item 2


1.  Item 1
2.  Item 2
    a.  Sub Item 1
    b.  Sub Item 2
3.  Item 3

Table in the document  

| Table | Header |
|-------|--------|
|cell1  | cell 2 |
|cell 3 | cell 4 |

the code block:

```{r}
paste("Hello","World!")
```

inline R code: `r paste("Hello","World!")` to add.  
Inline code not executed: `paste("Hello", "World")`

echo = TRUE the source code from being displayed

```{r}
dim(iris)
```

echo = FALSE will prevent the source code from being displayed

```{r echo=FALSE}
dim(iris)
```


Mathematical Equations or symbols

subscript: $X_a$

superscript: $X^{2}$

adding the integral with the range $\int_0^x x^2 dx$

Fraction: $\frac{x}{y}$

square root: $\sqrt{x}$

nth root: $\sqrt[n]{x}$

Summation sign: Formula for mean $\sum_{i=1}^n \frac{x_i*f_i}{f_i}$

$\prod_{k=1}^n$

degree $^{\circ}$ Temperature: $15^{\circ}C$

$\infty$

$\theta$

no option

```{r}
x <- 1:10
x
```

echo = FALSE

```{r echo = FALSE}
x <- 1:10
x
```

comment = NA

```{r comment=NA}
x <- 1:10
x
```


comment = '#', prompt = TRUE

```{r comment='#', prompt=TRUE}
x <- 1:10
x
```

echo = FALSE, fig.height = 4, fig.width = 4

```{r echo=FALSE, fig.width=4, fig.height=4}
y <- 10:1
x <- 1:10
plot(x,y)
```


```{r comment= "#"}
Lmodel <- lm(Petal.Width ~ Petal.Length,
             data = iris)

plot(iris$Petal.Length, iris$Petal.Width,
     col = "red",
     xlab = "Petal Length",
     ylab = "Petal Width",
     pch = 16)
grid()
abline(Lmodel,
       col = "blue",
       lwd = 2)


```